### 2023-01-26 code/1_exclusions_exploratory/1_exclusionsCN.Rmd
changed analysis to exploratory version

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_att_M$subject)

ppts_resp_M <- unique(df.resp_M$subject)
```

@@

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0.01086

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_M <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & demog_response > 4)

df.lang_ud_vi_M <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & demog_response > 4)

@@

ppts_en_speaker_M = unique(df.lang_en_M$subject) #74
percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0.375 # do not use this criterion

@@

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
percent_dropped #0.163043

@@

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
percent_dropped #0.0434782

df.resp_M <- df.resp_M %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_vi_speaker_M), 
         !(subject %in% ppts_lived_abroad_M), 
         !(subject %in% ppts_oversea_exp_M))

length(unique(df.resp_M$subject)) #149
```

```{r}
df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_M$subject))),
                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_M$subject))), 
                      ppts_after_demog_excl = c(length(unique(df.resp_M$subject))))
```

```{r}
write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataCN_excl_metadata.csv")
```

>>>>

df.ppts_att_M <- df.resp_M %>% #166
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_M_aft_attn <- df.resp_M %>% #38841
  filter(subject %in% df.ppts_att_M$subject)

ppts_resp_M_aft_attn <- unique(df.resp_M$subject)
```

@@

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.015

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_M <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & as.numeric(demog_response) > 4)

df.lang_ud_vi_M <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & as.numeric(demog_response) > 4)

@@

ppts_en_speaker_M = unique(df.lang_en_M$subject) #79
percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.385 # do not use this criterion

@@

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.185

@@

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.06

df.resp_M_aft_demog <- df.resp_M_aft_attn %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_vi_speaker_M), 
         !(subject %in% ppts_lived_abroad_M), 
         !(subject %in% ppts_oversea_exp_M))

length(unique(df.resp_M_aft_demog$subject)) #149
```

```{r}
df.demog_metadata <- data.frame(
  country = c("China"),
  ppts_finished = c(length(unique(df.ppts_finished_M$subject))),
  ppts_att_check_excl = c(length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))), 
  ppts_after_att_check_excl = c(length(unique(df.ppts_att_M$subject))),
  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_M),"*")), 
  ppts_en_speaker = c(length(ppts_en_speaker_M)), 
  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_M),"*")),
  ppts_zh_speaker = c("N/A"), 
  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_M),"*")), 
  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_M), "*")),
  ppts_after_demog_excl = c(length(unique(df.resp_M_aft_demog$subject))))
```

```{r}
write.csv(df.resp_M_aft_demog, "../../data/responding/exploratory/dataCN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/exploratory/dataCN_excl_metadata.csv")
```

### 2023-01-26 code/1_exclusions_exploratory/1_exclusionsUS.Rmd
changed analysis to exploratory version

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

@@

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #2
percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.01149425

@@

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.1436782

@@

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #36
percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.166667

@@

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #95
percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E_aft_attn)) / length(unique(df.resp_E_aft_attn$subject))
percent_dropped #0.4425287 # will not use this criterion

@@

length(unique(df.resp_E_aft_demog$subject)) #124

@@

```{r}
write.csv(df.resp_E_aft_demog, "../../data/responding/dataUS_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
```

>>>>

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

@@

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.02083333

@@

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #35
percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.1822917

@@

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #33
percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.171875

@@

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #91
percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E_aft_attn)) / length(unique(df.resp_E_aft_attn$subject))
percent_dropped #0.4739583 # will not use this criterion

@@

length(unique(df.resp_E_aft_demog$subject)) #119

@@

```{r}
write.csv(df.resp_E_aft_demog, "../../data/responding/exploratory/dataUS_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/exploratory/dataUS_excl_metadata.csv")
```

### 2023-01-26 code/1_exclusions_exploratory/1_exclusionsVN.Rmd
changed analysis to exploratory version

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73

ppts_resp_V <- unique(df.resp_V$subject) #137
```

@@

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0

#fluent in Vietnamese & Mandarin
df.lang_sp_en_V <- df.demog %>%
  filter(demog_question == "lang_sp_en" & demog_response > 4)

df.lang_ud_en_V <- df.demog %>%
  filter(demog_question == "lang_ud_en" & demog_response > 4)

@@

ppts_en_speaker_V = unique(df.lang_en_V$subject) #119
percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0.6277 # do not use this criterion

df.lang_sp_zh_V <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & demog_response > 4)

df.lang_ud_zh_V <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & demog_response > 4)

@@

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.05839416

@@

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #20
percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.109

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V), 
         !(subject %in% ppts_oversea_exp_V))

length(unique(df.resp_V$subject)) #110
```

```{r}
df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_V$subject))), 
                      ppts_after_demog_excl = c(length(unique(df.resp_V$subject))))
```

```{r}
write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataVN_excl_metadata.csv")
```

>>>>

df.resp_V_aft_attn <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73

ppts_resp_V_aft_attn <- unique(df.resp_V$subject) #137
```

@@

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.01005

#fluent in Vietnamese & Mandarin
df.lang_sp_en_V <- df.demog %>%
  filter(demog_question == "lang_sp_en" & as.numeric(demog_response) > 4)

df.lang_ud_en_V <- df.demog %>%
  filter(demog_question == "lang_ud_en" & as.numeric(demog_response) > 4)

@@

ppts_en_speaker_V = unique(df.lang_en_V$subject) #127
percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.623156 # do not use this criterion

df.lang_sp_zh_V <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & as.numeric(demog_response) > 4)

df.lang_ud_zh_V <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & as.numeric(demog_response) > 4)

@@

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.08542714

@@

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #18
percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.09547739

df.resp_V_aft_demog <- df.resp_V_aft_attn %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V), 
         !(subject %in% ppts_oversea_exp_V))

length(unique(df.resp_V_aft_demog$subject)) #110
```

```{r}
df.demog_metadata <- data.frame(
  country = c("Vietnam"),
  ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
  ppts_att_check_excl = c(length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))), 
  ppts_after_att_check_excl = c(length(unique(df.ppts_att_V$subject))),
  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_V),"*")), 
  ppts_en_speaker = c(paste(length(ppts_en_speaker_V))), 
  ppts_vi_speaker = c("N/A"),
  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_V),"*")), 
  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_V),"*")), 
  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_V), "*")),
  ppts_after_demog_excl = c(length(unique(df.resp_V_aft_demog$subject))))
```

```{r}
write.csv(df.resp_V_aft_demog, "../../data/responding/exploratory/dataVN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/exploratory/dataVN_excl_metadata.csv")
```

### 2023-01-26 code/2_combine/2_combine_exploratory.Rmd
changed analysis to exploratory version

```{r loading data E, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/responding/dataUS_excl.csv") %>%
  select(-X)
```

```{r loading data V, include=F}
df.resp_V <- read.csv("../../data/responding/dataVN_excl.csv") %>%
  select(-X)
```

```{r loading data M, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/responding/dataCN_excl.csv") %>%
  select(-X)
```

@@

df_main_analysis <- df #keep a copy of df in case exploratory analysis changes it
write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI.csv", row.names = F)
write.csv(triads_omit, "../../data/triads_omit.csv", row.names = F)
```

>>>>

```{r loading data E, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/responding/exploratory/dataUS_excl.csv") %>%
  select(-X)
```

```{r loading data V, include=F}
df.resp_V <- read.csv("../../data/responding/exploratory/dataVN_excl.csv") %>%
  select(-X)
```

```{r loading data M, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/responding/exploratory/dataCN_excl.csv") %>%
  select(-X)
```

@@

df_main_analysis <- df #keep a copy of df in case exploratory analysis changes it
write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI_exploratory.csv", row.names = F)
#write.csv(triads_omit, "../../data/triads_omit.csv", row.names = F)
```
